---
title: "Week 02: COVID Visualization Activity"
date: "September, 11 2023"
author: "Cuiyan Hua"
---

Today, we'll be working with a data set related to COVID.
This data is based on data from the the [COVID Tracking Project](https://covidtracking.com/).
I cleaned up this data and also added total populations from the 2020 for each of the relevant categories.
Note, due to differences in the way race and ethnicity are encoded in the census as compared to the the COVID Tracking Project, the population counts for LatinX may be somewhat inaccurate.

```{r load_data}
library(tidyverse)
load("CRDT Data.RData")
ls()
```

I've include 4 different data sets.
They all have the same data but have it represented in different ways.
Try using the different data sets and see which ones are good for making which plots.


```{r first_plot}
ggplot(covid_data_count, aes(x = date, y = Deaths)) + 
  geom_smooth()
```

If you want to only look at a specific state, you can do it like this.
For now, see what you can do just using `ggplot`.

```{r}
covid_data_count |> 
  filter(state == "MA") |> 
  ggplot(aes(x = date, y = Cases, color = race)) + geom_line()
```

1. Write code for a plot and describe what you observe?
ggplot(covid_data_count, aes(x = date, y = Deaths)) + 
  geom_smooth()
  
I plot in data to see the correlation between cases and death and found out that as the date goes on, it has more death during Covid-19.


2. Are there any conclusions you can draw?
We have a positive relationship between date and death. 


3. What were you not able to do due to not having the R knowledge?
I am not able to create multiple graphs shown at the same time to try to compare which one is better


4. What other data would be useful to better understand this data?
Additional data related to factors such as vaccination rates, hospitalization rates, and public health measures could be valuable for a comprehensive analysis of the COVID-19 situation. 

